The \dealii Library, Version 9.2

### 2020-05-23 9.2/paper.tex
Small fixes in simd section

Up to release 9.1, the
vector length $n$ has been set at compile time of the library to the highest
possible value supported by the given processor architecture.
Now, a second optional template argument
\texttt{VectorizedArray<Number, size>} can be given with \texttt{size} explicitly controlling
the vector length within the capabilities of a particular instruction set.
A full list of supported
vector lengths is presented in Table~\ref{tab:vectorizedarray}.
\todo[inline]{This table lacks the AltiVec support}

@@

\begin{table}
\caption{Supported vector lengths of the class \texttt{VectorizedArray} and
the corresponding instruction-set-architecture extensions. }\label{tab:vectorizedarray}
\centering
\begin{tabular}{ccc}
\toprule
\textbf{double} & \textbf{float} & \textbf{ISA}\\
\midrule
VectorizedArray<double, 1> & VectorizedArray<float, 1> & (auto-vectorization) \\
VectorizedArray<double, 2> & VectorizedArray<float, 4> & SSE2 \\
VectorizedArray<double, 4> & VectorizedArray<float, 8> & AVX/AVX2 \\
VectorizedArray<double, 8> & VectorizedArray<float, 16> & AVX-512 \\
\bottomrule
\end{tabular}

\caption{Comparison of relevant SIMD-related classes in deal.II and C++20.}\label{tab:simd}
\centering
\begin{tabular}{cc}
\toprule
\textbf{VectorizedArray (deal.II)} & \textbf{std::simd (C++20)} \\
\midrule
VectorizedArray<Number> & std::experimental::native\_simd<Number> \\
VectorizedArray<Number, size> & std::experimental::fixed\_size\_simd<Number, size> \\ \bottomrule
\end{tabular}
\end{table}

Furthermore, the new interfaces enable using any data structure
\texttt{VectorizedArrayType} as long as it supports required
functionalities like \texttt{size()} or \texttt{value\_type}. This prepares
for the \texttt{C++23} feature \texttt{std::simd} that will be enabled in the future.
Table~\ref{tab:simd} gives a comparison of the deal.II-specific SIMD classes and
the equivalent C++20 classes. Finally, this change also prepares for specialized
code paths exploiting
vectorization within an element~\cite{KronbichlerKormann2019} in the future.

>>>>

Up to release 9.1, the
vector length $n$ has been set at compile time of the library to the highest
possible value supported by the given processor architecture.
Now, a second optional template argument
\texttt{VectorizedArray<Number, size>} can be given with \texttt{size} explicitly controlling
the vector length within the capabilities of a particular instruction set.
A full list of supported
vector lengths is presented in Table~\ref{tab:vectorizedarray}.

@@

\begin{table}
\caption{Supported vector lengths of the class \texttt{VectorizedArray} and
the corresponding instruction-set-architecture extensions. }\label{tab:vectorizedarray}
\centering
\begin{tabular}{ccc}
\toprule
\textbf{double} & \textbf{float} & \textbf{ISA}\\
\midrule
VectorizedArray<double, 1> & VectorizedArray<float, 1> & (auto-vectorization) \\
VectorizedArray<double, 2> & VectorizedArray<float, 4> & SSE2/AltiVec \\
VectorizedArray<double, 4> & VectorizedArray<float, 8> & AVX/AVX2 \\
VectorizedArray<double, 8> & VectorizedArray<float, 16> & AVX-512 \\
\bottomrule
\end{tabular}

\caption{Comparison of relevant SIMD-related classes in deal.II and \texttt{C++23}.}\label{tab:simd}
\centering
\begin{tabular}{cc}
\toprule
\textbf{VectorizedArray (deal.II)} & \textbf{std::simd (\texttt{C++23})} \\
\midrule
VectorizedArray<Number> & std::experimental::native\_simd<Number> \\
VectorizedArray<Number, size> & std::experimental::fixed\_size\_simd<Number, size> \\ \bottomrule
\end{tabular}
\end{table}

Furthermore, the new interfaces enable using any data structure
\texttt{VectorizedArrayType} as long as it supports required
functionalities like \texttt{size()} or \texttt{value\_type}. This prepares
for the \texttt{C++23} feature \texttt{std::simd} that will be enabled in the future.
Table~\ref{tab:simd} gives a comparison of the deal.II-specific SIMD classes and
the equivalent \texttt{C++23} classes. Finally, this change also prepares for specialized
code paths exploiting
vectorization within an element~\cite{KronbichlerKormann2019} in the future.
